---
title: "Week 01: Introduction to R and R-Markdown"
author: "you"
date: "2024-01-05"
output:
  html_document:
    theme: flat
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
editor_options:
  chunk_output_type: console
---

# Introduction

Packages.

```{r setup, include=FALSE}
#install.packages("tidyverse")
library(tidyverse)
```

The `tidyverse` package just loads many different packages at once:

* ggplot2 - charts and plots
* dplyr - chaining data manipulation (filtering, mutation, reshaping)
* tibble - for effective data tables
* tidyr - helpful functions for cleaning data
* readr - functions for reading and writing data
* purrr - functional programming tools
* stringr - for manipulating text and character strings
* forcats - for dealing with categorical or ordinal data (factors)

Summarize data. The data `mtcars` is available in the base version of R.

```{r mtcars}
summary(mtcars)
```

# Including Plots

You can also embed plots, for example:

```{r displacement_mpg, echo=FALSE}
ggplot(mtcars, aes(x = disp, y = mpg)) +
  geom_point()
```
